\subsection{Code of Ethics}

\begin{remark} \hlt{Preamble}\\
The CFA Institute Code of Ethics and Standards of Professional Conduct are fundamental to the values of CFA Institute and essential to achieving its mission to lead the investment profession globally by promoting the highest standards of ethics, education, and professional excellence for the ultimate benefit of society. High ethical standards are critical to maintaining the public’s trust in financial markets and in the investment profession.\\
Since their creation in the 1960s, the Code and Standards have promoted the integrity of CFA Institute members and served as a model for measuring the ethics of investment professionals globally, regardless of job function, cultural differences, or local laws and regulations.\\
All CFA Institute members (including holders of the Chartered Financial Analyst [CFA] designation) and CFA candidates have the personal responsibility to embrace and uphold the provisions of the Code and Standards and are encouraged to notify their employer of this responsibility. Violations may result in disciplinary sanctions by CFA Institute. Sanctions can include revocation of membership, revocation of candidacy in the CFA Program, and revocation of the right to use the CFA designation.
\end{remark}

\begin{definition} \hlt{Code of Ethics}\\
Members of CFA Institute (including CFA charter-holders) and candidates for the CFA designation (“Members and Candidates”) must:
\begin{enumerate}[label=\roman*.]
\setlength{\itemsep}{0pt}
\item Act with integrity, competence, diligence, and respect and in an ethical manner with the public, clients, prospective clients, employers, employees, colleagues in the investment profession, and other participants in the global capital markets.
\item Place the integrity of investment profession and interests of clients above their own personal interests.
\item Use reasonable care and exercise independent professional judgment when conducting investment analysis, making investment recommendations, taking investment actions, engaging in other professional activities.
\item Practice and encourage others to practice in a professional and ethical manner that will reflect credit on themselves and the profession.
\item Promote the integrity and viability of the global capital markets for the ultimate benefit of society.
\item Maintain and improve their professional competence and strive to maintain and improve the competence of other investment professionals.
\end{enumerate}
\end{definition}